Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-12 jessie-writeup/jessie-writeup.tex
Cyclic proof of TFAE statement

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\aff}{\text{aff}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\mathrm{strip}}

@@

\begin{notation}
  Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
  \raft{Let's use $\preceq$ instead of $\leq$, since it's clearly different from the usual $\leq$, and easier to find--replace later.}
\end{notation}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
%	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}\raft{Confused by BR}

@@

@@

\section{Main statement}

\begin{proposition}\label{prop:optimal-reports-per-level-set}
  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.

  The following are equivalent:
  \begin{enumerate}
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\trim(\Gamma)$ is finite.
  \item $\strip(\Gamma)$ is finite.
  \item \jessie{Added after fplc-elic.tex}
	\begin{itemize}
		\item[4.] $\trim(\Gamma)$ is finite and elicitable.
		\item[5.] There is a finite set of full dimensional level sets that union to $\P$.
		\item[6.] There is a property $\Gamma': \P \toto \R$ such that there is a subset $\R'\subseteq\reals^d$ and bijection $\varphi:\R'\to\R$ such that $r'\in\Gamma(p) \cap \R' \iff \varphi(r') \in \Gamma'(p)$.
	\end{itemize}
  \end{enumerate}
\end{proposition}

\begin{proof}
First, we show $2 \iff 3$ then proceed in different directions to show $1\implies 2$ and $2 \implies 1$, or something like that.
Then we add some more to supplement, like $4 \iff 2$.

\begin{enumerate}
	\item [$3 \implies 2$]
	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.

	\item[$2 \implies 3$] 
	Consider $\trim(\Gamma)$ to be finite.
%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.

	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_r$ for $r \in \R$.
	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
	%\jessie{Need argument about how we can only have level sets on the boundary.}

@@

\item [$1 \implies 2$]
Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \preceq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.

Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e. full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
Therefore, $\trim(\Gamma)$ is finite.

\item [$2 \implies 1$]
Consider $\trim(\Gamma) = \Theta$.
$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.
%Additionally, for every $\theta \in \strip(\Gamma')$, there is an $r \in \R'$ so that $\{r\} = \Gamma(p)$ for all $p \in \inter{\theta}$ by nonredundancy of $\Gamma'$ and .

@@

\item[$4 \implies 2$] Trivial
\item[$2 \implies 4$] 
Let $\Theta := \trim(\Gamma)$ be finite and $\Gamma$ elicited by the loss $L$.
Construct $\R'$ as in Conjecture~\ref{conj:gam-prime-exists}.
Restricting the loss $L|_{\R'}$ should then elicit $\trim(\Gamma)$.
Fix some $\theta \in \Theta$.
\jessie{TODO... I'm a little unclear here if I should show there's a report that minimizes the loss or a subgradient set that corresponds to each level set $\theta \in \Theta$, and thus, a labeling}

\item[$1\implies 5$] Trivially, if $\trim(\Gamma)$ is finite and elicitable, then $\trim(\Gamma)$ is finite.
\item[$5 \implies 2$] Consider a finite set of full dimensional level sets that union to $\P$: call it $S$.
If we show $\trim(\Gamma) \subseteq S$, then $S$ finite $\implies \trim(\Gamma)$ finite.
Consider some $\theta \in \trim(\Gamma)$.
Then $\theta$ is full dimensional by Conjecture~\ref{conj:trim-full-dim}, so we conclude $\theta \in S$.
Therefore, $\theta \in \trim(\Gamma) \implies \theta \in S$, so $\trim(\Gamma) \subseteq S$, and therefore $\trim(\Gamma)$ is finite.

%\item[$2 \implies 1$]  
%\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}
%
%Let $\Theta := \trim(\Gamma)$ be a finite set.
%By Conjecture~\ref{conj:gam-prime-exists}, there is then a nonredundant, nondegenerate property $\Gamma'$ such that $\strip(\Gamma') = \trim(\Gamma)$.
%Let $\R' \subseteq \R$ be the finite set used to define the property $\Gamma'$.
%
%As $\Theta$ is finite and $\trim(\Gamma)$ is the set of full dimensional level sets of $\Gamma$, the finite number of full-dimensional level sets follows from the assumption and definitions combined.
%
%Consider a level set $\theta\in \Theta$.
%There is a report $r \in \R'$ so that $\Gamma'(p) = \{r\}$ for all $p \in \inter{\theta}$; this follows from nonredundancy of $\Gamma'$.
%
%Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
%\jessie{Uniqueness actually follows from concavity of Bayes Risk, since the measure of the sets with multiple viable labels has to be of measure zero, and can't be full dimensional.}
%
%
%%Let $\Theta := \trim(\Gamma)$ be a finite set.
%%By construction, $\Theta$ is a set of full dimensional level sets defining the property $\Gamma$.
%%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
%%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \preceq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
%%
%%Consider a level set $\theta \in \Theta$.
%%We want to show there is a unique $r \in \R'$ such that $\Gamma(p) = \{r\}$ for all $p \in \inter{\theta}$.
%%
%%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \preceq \Gamma$.
%%Fix some level set $\theta \in \Theta$.
%%For any $p \in \inter{\theta}$, there is then a report $r \in \R'$ such that  $r \in \Gamma(p)$ by nondegeneracy of $\Gamma'$.
%%We then want to show $r$ is unique.
%%
%%For contradiction, consider some $r' \in \R'$ such that $r \neq r'$.
%%As $\trim(\Gamma) = \strip(\Gamma')$ contains only full dimensional level sets, then $\Gamma_r$ and $\Gamma_{r'}$ are both full dimensional, as is their intersection $\Gamma_r \cap \Gamma_{r'}$.
%%Since we define $\Gamma'$ in a manner so that for all $r \in \R' \implies \Gamma_r = \Gamma'_r$, we then say $\Gamma_r \cap \Gamma_{r'} = \Gamma'_r \cap \Gamma'_{r'}$, which contradicts the nonredundancy of $\Gamma'$.
%%Therefore we observe a contradiction, and conclude $r = r'$.
%%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.

\end{enumerate}

@@

>>>>

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\aff}{\text{aff}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\card}{\textbf{card}}

@@

\begin{notation}
  Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
  \jessiet{Changed $\R \subseteq \R$ to $\R' \subseteq \varphi(\R)$.}
\end{notation}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
%	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable a.e.}\raft{Confused by BR}

@@

\begin{conjecture}\label{conj:lev-sets-subsets}
	Let the elicitable property $\Gamma$ embed the nondegenerate property $\gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
\end{conjecture}

\begin{proof}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $p \in \Gamma_r \implies \exists r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.

	Consider $p \in \Gamma_r$.
	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r' = \varphi(r) \in \gamma(p)$ and $r' \in \R'$.
	We then know that $p \in \gamma_{r'}$.
	Now suppose $q \in \Gamma_r$ and $\varphi(r) = r_1 \neq r'$.
	Therefore, $q \not \in \gamma_{r'}$, which contradicts the the fact that $\Gamma$ embeds $\gamma$.
	Thus, there must be an $r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.

	Therefore, every level set of the property $\Gamma$ is a subset of a level set of $\gamma$.
\end{proof}

@@

\section{Defining embeddability}

\begin{proposition}\label{prop:optimal-reports-per-level-set}
  Let $\Gamma:\P\toto\R$ be a non-degenerate elicitable property.

  The following are equivalent:
  \begin{enumerate}
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\trim(\Gamma)$ is finite.
  \item $\strip(\Gamma)$ is finite.
  \item \jessie{Added after fplc-elic.tex}
	\begin{itemize}
		\item[4.] $\trim(\Gamma)$ is finite and elicitable.
		\item[5.] There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
		\item[6.] There is a nondegenerate, finite property $\Gamma':\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\Gamma'$)
	\end{itemize}
  \end{enumerate}
\end{proposition}

\begin{proof}
First, we show $2 \iff 3$ then proceed in a cycle to show $6 \implies 1 \implies 5 \implies 4 \implies 2 \implies 6$.

\begin{enumerate}
%%%	\item [$3 \implies 2$]
%%%	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.

	\item[$2 \iff 3$] 
	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.
	Thus we just show $2 \implies 3$.

	Consider $\trim(\Gamma)$ to be finite.
%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.
	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_r$ for $r \in \R$.
	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
	%\jessie{Need argument about how we can only have level sets on the boundary.}

@@

%%%\item [$1 \implies 2$]
%%%Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \preceq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
%%%
%%%Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
%%%Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e. full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
%%%(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
%%%Therefore, $\trim(\Gamma)$ is finite.

%%% means taken out to reduce space and make the proof a loop
%%%\item [$2 \implies 1$]
%%%Consider $\trim(\Gamma) = \Theta$.
%%%$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
%%%Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
%%%Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
%%%Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.

@@

%%%\item[$2 \implies 4$] \jessie{Shown in cvx-fin-notes.tex}
%Let $\Theta := \trim(\Gamma)$ be finite and $\Gamma$ elicited by the loss $L$.
%Construct $\R'$ as in Conjecture~\ref{conj:gam-prime-exists}.
%Restricting the loss $L|_{\R'}$ should then elicit $\trim(\Gamma)$.
%\jessie{TODO... I'm a little unclear here if I should show there's a report that minimizes the loss or a subgradient set that corresponds to each level set $\theta \in \Theta$, and thus, a labeling}

%%%\item[$5 \implies 2$] Consider a finite set of full dimensional level sets that union to $\P$: call it $S$.
%%%If we show $\trim(\Gamma) \subseteq S$, then $S$ finite $\implies \trim(\Gamma)$ finite.
%%%Consider some $\theta \in \trim(\Gamma)$.
%%%Then $\theta$ is full dimensional by Conjecture~\ref{conj:trim-full-dim}, so we conclude $\theta \in S$.
%%%Therefore, $\theta \in \trim(\Gamma) \implies \theta \in S$, so $\trim(\Gamma) \subseteq S$, and therefore $\trim(\Gamma)$ is finite.

\item[$6 \implies 1$] 
Let the elicitable property $\Gamma$ embed some finite property $\gamma$.
Then since $\gamma$ is a finite set of level sets, and every level set of $\Gamma$ is a subset of a level set of $\gamma$ by Conjecture~\ref{conj:lev-sets-subsets}.

Consider the finite set $\R'$ to be the range of $\gamma$.

By Conjecture~\ref{conj:prec-if-embeds}, since $\Gamma$ embeds $\gamma$, we know that $\gamma \preceq \Gamma$, so $\Theta = \strip(\gamma) = \trim(\Gamma)$ is finite and every $\theta \in \Theta$ is full dimensional.
Since $\Gamma$ is elicitable, the optimal report $r_\theta \in \Gamma(p)$ is unique almost everywhere on $\P$ (by differentiability of the score $G$ almost everywhere).
Additionally, as $\gamma$ is nondegenerate, its level sets union to $\P$.

For each level set $\theta \in \Theta$, there is a unique optimal report $\{r_\theta \} = \Gamma(p)$ for all $p \in \inter{\theta}$ by the elicitability of $\Gamma$.
This can be seen by the differentiability of $G$ almost everywhere in $\P$, and thus uniqueness of $\Gamma(p)$ almost everywhere.
A convex level set with nonempty interior has positive measure, so if $r_\theta$ was not unique on the interior of $\theta$, the set where $r_\theta$ is not unique would have positive measure, contradicting elicitability of $\Gamma.$

Therefore the set $\Theta = \{\gamma_r : r \in \R' \} = \trim(\Gamma) \subseteq \strip(\Gamma)$ is a finite set of full dimensional level sets that union to $\P$ with a unique optimal report on the interior of each level set. 
\item[$1 \implies 5$] Trivial
\item[$5 \implies 4$]
Let $\Theta$ be a set of full-dimensional level sets of $\Gamma$ that union to $\P$.
First, we know $\Gamma$ is nondegenerate.

The $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists} has a finite codomain $\R'$ since $\R'$ is the set defined by the unique optimal report defined on the interior of each level set.
Since there are only finitely many full-dimensional level sets, the set $\R'$ is finite.

We then know by definition of $\trim$ that since $\Gamma'$ is nonredundant, nondegenerate, and $\Gamma' \preceq \Gamma$, that $\strip(\Gamma') = \trim(\Gamma)$ is finite.

Therefore $\trim(\Gamma)$ is finite, and $L|_\R$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

\item[$4 \implies 2$] Trivial
\item[$2 \implies 6$] Let $\trim(\Gamma)$ be finite.
Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$.

Then we want to show $\Gamma$ embeds $\gamma$.
Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R) \jessie{?= \card(\reals^d)}$, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.

Consider some $r \in \gamma(p)$.
Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) = \Gamma(p)$.
\jessie{Hand wavvy there}

Now consider $\varphi(r) \in \Gamma(p)$.
Take the right inverse (well-defined since $\varphi$ is an injection) and observe that $r \in \varphi^{-1}(\Gamma(p) \cap \R') = \gamma(p)$ since $\gamma$ is nondegenerate.

Therefore, $2 \implies 6$.

%\item[$2 \implies 1$]  
%\emph{Assumptions used: Nondegeneracy, elicitability of $\Gamma$}
%
%Let $\Theta := \trim(\Gamma)$ be a finite set.
%By Conjecture~\ref{conj:gam-prime-exists}, there is then a nonredundant, nondegenerate property $\Gamma'$ such that $\strip(\Gamma') = \trim(\Gamma)$.
%Let $\R' \subseteq \R$ be the finite set used to define the property $\Gamma'$.
%
%As $\Theta$ is finite and $\trim(\Gamma)$ is the set of full dimensional level sets of $\Gamma$, the finite number of full-dimensional level sets follows from the assumption and definitions combined.
%
%Consider a level set $\theta\in \Theta$.
%There is a report $r \in \R'$ so that $\Gamma'(p) = \{r\}$ for all $p \in \inter{\theta}$; this follows from nonredundancy of $\Gamma'$.
%
%Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
%\jessie{Uniqueness actually follows from concavity of Bayes Risk, since the measure of the sets with multiple viable labels has to be of measure zero, and can't be full dimensional.}
%
%
%%Let $\Theta := \trim(\Gamma)$ be a finite set.
%%By construction, $\Theta$ is a set of full dimensional level sets defining the property $\Gamma$.
%%Thus, $\Gamma$ then only has finitely many \emph{full-dimensional} level sets.
%%Then there is a finite set $\R' \subseteq \R$ defined by the property $\Gamma' \preceq \Gamma$ where $\strip(\Gamma') = \trim(\Gamma)$.\jessie{Make sure I can claim this.}
%%
%%Consider a level set $\theta \in \Theta$.
%%We want to show there is a unique $r \in \R'$ such that $\Gamma(p) = \{r\}$ for all $p \in \inter{\theta}$.
%%
%%Take the finite set $\R' \subseteq \R$ such that the nondegenerate, nonredundant property $\Gamma' \preceq \Gamma$.
%%Fix some level set $\theta \in \Theta$.
%%For any $p \in \inter{\theta}$, there is then a report $r \in \R'$ such that  $r \in \Gamma(p)$ by nondegeneracy of $\Gamma'$.
%%We then want to show $r$ is unique.
%%
%%For contradiction, consider some $r' \in \R'$ such that $r \neq r'$.
%%As $\trim(\Gamma) = \strip(\Gamma')$ contains only full dimensional level sets, then $\Gamma_r$ and $\Gamma_{r'}$ are both full dimensional, as is their intersection $\Gamma_r \cap \Gamma_{r'}$.
%%Since we define $\Gamma'$ in a manner so that for all $r \in \R' \implies \Gamma_r = \Gamma'_r$, we then say $\Gamma_r \cap \Gamma_{r'} = \Gamma'_r \cap \Gamma'_{r'}$, which contradicts the nonredundancy of $\Gamma'$.
%%Therefore we observe a contradiction, and conclude $r = r'$.
%%Therefore, if $\trim(\Gamma)$ is finite, then the property $\Gamma$ has a finite set (namely, $\trim(\Gamma)$) of full dimensional level sets so that for every $\theta \in \Theta$, there is a unique optimal report $r$ for every $p \in \inter{\theta}$.
\end{enumerate}

@@

\begin{conjecture}\label{conj:prec-if-embeds}
	If the elicitable property $\Gamma$ embeds the nondegenerate finite $\gamma$, then $\gamma \preceq \Gamma$ and $\trim(\Gamma) = \strip(\gamma)$.
\end{conjecture}
\begin{proof}

	By assumption, $\gamma$ is nongenerate.

	To show $\gamma \preceq \Gamma$, we know that since $\Gamma$ embeds $\gamma$, there is an injection $\varphi : \R' \to \R$ so that $r' \in \gamma(p) \iff \varphi(r') \in \Gamma(p)$.
	As $\varphi(\R') \subseteq \R$ and $\gamma$ is nondegenerate, we know that for all $r \in \R'$

	Therefore, $\gamma(p) = \Gamma(p) \cap \R'$

	Finally, we show $\gamma$ is nonredundant. \jessie{TODO...}

	Since $\gamma \preceq \Gamma$ and $\gamma$ is nondegenerate and nonredundant, we apply Lemma~\ref{lem:define-trim} to observe $\trim(\Gamma) = \strip(\gamma)$.
\end{proof}
